Topic 21 Experiment and analysis

### 2018-05-17 Meetings/AnalysisMeetingMay2018/analysis_meeting2018_topic21.tex
Added figure,scripts and TeX
For analysis meeting of 17 of May

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{../biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21 Experiment and analysis}
\date{17 May 2018}
\author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
  scientific team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov,
Jernej Kovacic, Benoît Labit, Bruce Lipschultz, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
j\end{frame}

@@

@@

      \includegraphics<1>[width=\textwidth]{~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}

@@

            different current.}
          \item \textcolor{ta3chameleon}{Still some inconsistency at lower
            current in agreement with different detachment evolution}}}

@@

      \includegraphics<1>[width=\textwidth]{~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}

@@

      \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationGreenwaldConstantQ95}
      \includegraphics<6>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantQ95}

@@

            upstream profile modification}  

@@

% %% H-Mode same fueling

@@

            fueling as \# 34276 but with the cryompump}

@@

            pressure as \# 34276}

@@

% \begin{frame}{Conclusion}
%   \Fontvi
%   \begin{itemize}
%     \item Current scan at constant B$_t$ and at constant q$_{95}$
%       performed during density ramps L-Mode experiments both at AUG
%       and TCV
%     \item In both the case shoulder appear earlier in density at lower
%       current but AUG shows reconciliation of behavior if considered
%       as a function of greenwald fraction and $\Lambda_{div}$
%     \item Both the experiments exhibit at constant B$_t$ flattening of the profile as
%       blob size is increasing, independently from the current. The
%       same behavior is observed during current scan at constant
%       q$_{95}$ \alert{only on AUG}
%     \item On TCV during the current scan at constant q$_{95}$
%       detachment not reached and this \alert{prevent upstream profile
%         flattening}
%     \item H-Mode experiments performed on AUG where fueling and
%       pumping have been varied. Proved inter-ELM profile flattening
%       also in H-Mode with a more efficient puffing without the
%       cryopump. \alert{Hints on the role of neutrals also in H-Mode}
%   \end{itemize}
% \end{frame}

% \begin{frame}{D$_{\alpha}$ tomography: work in progress}
% \Fontvi
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2000}
%       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2700}
%       \includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_3100}
%     \end{column}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%         \item \alert{Preliminary} results from inversion tomography
%           from calibrated D$_{\alpha}$ camera under the assumption of
%           toroidally symmetric emission limited to the region outside
%           the LCFS
%         \item \emph{Simultaneous Algebraic Reconstruction Technique
%             (SART) (A.H. Anderson and A.C.Kak,  Ultrasonic Imaging
%             \textbf{6},  81 (1984))}
%         \item<2-> As time evolves during the L-Mode ramp we observe
%           D$_{\alpha}$ radiation moving from HFS towards the LFS
%           common flux region
%         \item<3-> \alert{This is consistent with JET observation in
%             Horizontal target regime whenever shoulder is observed}
%       \end{itemize}
%     \end{column}
%   \end{columns}
% \end{frame}

>>>>

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{../biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21 Experiment and analysis}
\date{17 May 2018}
\author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
  scientific team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov,
Jernej Kovacic, Benoît Labit, Bruce Lipschultz, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
\end{frame}

@@

\begin{frame}{Devices, diagnostics and methods}
\only<1>{
  \centering{\includegraphics[width=0.8\textwidth]{../generalFigures/Divertor-AUG-TCV}}

  \begin{itemize}
    \item \textbf{AUG:} Metallic wall, cryopumps, closed divertor with
      SP on vertical target, short divertor leg
    \item \textbf{TCV:} Carbon wall, completely open divertor,
      operated with relative long divertor leg, no cryopump  
  \end{itemize}
}
\only<2>{
  \vspace{-1.5cm}
  \centering{\includegraphics[width=0.7\textwidth]{../generalFigures/ProbeHead}}
\Fontvi
  \begin{itemize}
    \item \textbf{AUG:} Ion saturation current measured at different
      radial/poloidal position to get velocity from 2D cross-correlation
    \item \textbf{TCV:} Only 1 j$_{sat}$ measurement available,
      different velocity estimate. $v_r$ from
      $\mathbf{E}\times\mathbf{B}$ evaluation from floating potentials
      on CAS, $v_z$ from 2D cross-correlation analysis

  \end{itemize}
}
\end{frame}

@@

      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}

@@

            different current.}}
          \item<only@10> \textcolor{ta3chameleon}{Still some inconsistency at lower
            current in agreement with different detachment evolution}}

@@

      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}

@@

      \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsGreenwaldConstantQ95}
      \includegraphics<6-7>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantQ95}

@@

            upstream profile modification}}  

@@

% % %% H-Mode same fueling

@@

            fueling as} \textcolor{colorA}{\# 34276} \textcolor{colorB}{but with the cryompump}

@@

            pressure as} \textcolor{colorA}{\# 34276}

@@

\begin{frame}{Conclusion}
  \Fontvi
  \begin{itemize}
    \item Current scan at constant B$_t$ and at constant q$_{95}$
      performed during density ramps L-Mode experiments both at AUG
      and TCV
    \item In both the case shoulder appear earlier in density at lower
      current but AUG shows reconciliation of behavior if considered
      as a function of greenwald fraction and $\Lambda_{div}$ for
      constant B$_t$ but not for constant q$_{95}$. AUG still well
      represented by $\Lambda_{div}$. \alert{Shoulder starts
        developing at the onset of highly recycling regime}
    \item Both the experiments exhibit at constant B$_t$ flattening of the profile as
      blob size is increasing, independently from the current. The
      same behavior is observed during current scan at constant
      q$_{95}$ \alert{only on AUG}
    \item On TCV during the current scan at constant q$_{95}$
      detachment not reached and this \alert{prevents upstream profile
        flattening}
    \item H-Mode experiments performed on AUG where fueling and
      pumping have been varied. \alert{Proved inter-ELM profile flattening
      also in H-Mode} \alert{but high neutral pressure (not only edge
      density) is needed}
  \item<2-> \textbf{\textcolor{ta3scarletred}{Can we find a different parameter to reconcile
        the experimental observation?}}
  \end{itemize}
\end{frame}

\begin{frame}{On going work}
  A series of works are still on-going \textcolor{ta3scarletred}{or
    yet to be started}
  \begin{itemize}[<+->]
    \item Neutral density estimate from light emission
      \textbf{M. Agostini}
    \item Wall embedded probe analysis \textbf{S. Costea,
        M. Spolaore}
    \item Shoulder from Reflectometry analysis \textbf{E. Sieglun}
    \item \textcolor{ta3scarletred}{SOLPS modelling AUG/TCV for modelling collisionality
      along flux tube and compare to measurement}
    \item \textcolor{ta3scarletred}{Balmer series analysis for
        recombination analysis on TCV \textbf{K. Verhaegh}}
  \item \textcolor{ta3scarletred}{HFSD}
    \item \textcolor{ta3scarletred}{\ldots}

  \end{itemize}
\end{frame}
% \begin{frame}{D$_{\alpha}$ tomography: work in progress}
% \Fontvi
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2000}
%       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2700}
%       \includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_3100}
%     \end{column}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%         \item \alert{Preliminary} results from inversion tomography
%           from calibrated D$_{\alpha}$ camera under the assumption of
%           toroidally symmetric emission limited to the region outside
%           the LCFS
%         \item \emph{Simultaneous Algebraic Reconstruction Technique
%             (SART) (A.H. Anderson and A.C.Kak,  Ultrasonic Imaging
%             \textbf{6},  81 (1984))}
%         \item<2-> As time evolves during the L-Mode ramp we observe
%           D$_{\alpha}$ radiation moving from HFS towards the LFS
%           common flux region
%         \item<3-> \alert{This is consistent with JET observation in
%             Horizontal target regime whenever shoulder is observed}
%       \end{itemize}
%     \end{column}
%   \end{columns}
% \end{frame}
